\documentclass[12pt]{letter}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \newcommand{\principalname}{Dr. ZZZ}
  \newcommand{\schoolname}{ZZZ High School}
  \newcommand{\schoolstreetaddress}{ZZZ}
  \newcommand{\schoolcitystate}{ZZZ, TX}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \usepackage[T1]{fontenc}
  \usepackage{geometry}
  \usepackage{hyperref}
  \usepackage{xcolor}
  \hypersetup{
      colorlinks,
      linkcolor={red!50!black},
      citecolor={blue!50!black},
      urlcolor={blue!80!black}
  }

  \geometry{letterpaper,tmargin=1.5in,bmargin=1in,lmargin=1.5in,rmargin=1.5in}

  %remove leading whitespace at the top of the first page
  \makeatletter
  \let\@texttop\relax
  \makeatother

  % move the date to the left side of the page
  \makeatletter
  \renewcommand*{\opening}[1]{\ifx\@empty\fromaddress
    \thispagestyle{firstpage}%
      {\raggedleft\@date\par}%
    \else  % home address
      \thispagestyle{empty}%
      {\raggedleft\begin{tabular}{l@{}}\ignorespaces
        \fromaddress \\*[2\parskip]%
        \end{tabular}\par
       \raggedright\@date\par}%
    \fi
    \vspace{2\parskip}%
    {\raggedright \toname \\ \toaddress \par}%
    \vspace{2\parskip}%
    #1\par\nobreak}
  \makeatother


  \signature{David A. Hasan}
  \address{%
    {\footnotesize\textsc{6103 Sun Vista}}\\
    {\footnotesize\textsc{Austin, TX 78749}}\\
    {\footnotesize{(512) 945-3271}}\\
    {\footnotesize\ttfamily \href{mailto:david@augerhandle.net}{david@augerhandle.net}}\\
    {\footnotesize\ttfamily \href{https://augerhandle.github.io/portfolio}{augerhandle.github.io/portfolio}}
  }

  \begin{document}
  \fontfamily{ppl}\selectfont
  \begin{letter}{\principalname\\ \schoolname \\ \schoolstreetaddress\\ \schoolcitystate}
  \opening{\principalname,}

  I am applying for a \textit{math teaching position} at \schoolname.
  My background is nontraditional.
  I am an aerospace engineer and software developer making a long--contemplated transition to teaching.

  I am currently enrolled in the
  \textit{Region 13 Educator Certification Program}.
  I have completed student teaching at AISD Akins High School
  and have passed the
  \textit{TExES ExCET Physics/Math 7--12} content exam.
  In addition, I taught several semesters of \textit{College Algebra} and \textit{Dynamics} 
  at Austin Community College many years ago,
  and for several years I have volunteered at AISD Clayton Elemetary
  working on science, math, software and poetry.

  Although I am relatively new to teaching,
  I believe that I will be an asset to your faculty for (at least) the following reasons.
  \begin{itemize}
    \item Due to my background in engineering and software development,
    I am extremely comfortable with math, physics and computer science.
    \item I have STEM career experiences and insights that I plan to use 
    to enrich my lessons and keep my students interested.
    \item The Region--13 certification program that I am enrolled in
    is aggressively focused on creating engaging lessons and (most importantly)
    managing the classroom by explicitly defining expectations and teaching
    class procedures and routines.
  \end{itemize}
    
    I have attached a resume.
    It summarizes my qualifications in more detail, including my
    education, certification, work history and references.

    More information about me is available 
    at the URL at the top of this letter. 
    That website hosts my 
    \textit{new teacher portfolio} where I am collecting my thoughts, initial plans, and 
    other details related to how I plan to hit the ground running in the fall.

    Thank you for your consideration.
    I look forward to hearing from you.

  \closing{Sincerely,}
  \encl{resume}
  \end{letter}
  \end{document}
