\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{xifthen}


\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{David A. Hasan}
\newcommand{\addr}{6103 Sun Vista, Austin, TX 78749}
\newcommand{\phone}{(512) 945-3271}
\newcommand{\email}{david@augerhandle.net}
\newcommand{\web}{https://augerhandle.github.io/portfolio}


% commands to change left/right margins
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments


\newcommand{\resheader}{
	\begin{center}
		\Huge\name
	\end{center}
	\vspace{-8pt} \rule{\textwidth}{1pt}
	\vspace{-8pt}
	{\small \textit{\addr} \hfill \texttt{\email}}\\
	{\vskip -6pt}{\small \textit{\phone} \hfill \texttt{\web}}
	{\vskip -6pt}\rule{\textwidth}{1pt}
}

\newcommand{\resabstract}[1]{
	\begin{changemargin}{.45in}{.45in}
		\textit{#1}
	\end{changemargin}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\rule{\textwidth}{0.25pt}	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 
	\textit{(#3)}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}
\newenvironment{reslistx}[2]{
	\resitem{\textbf{#1} --- #2}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

\resheader

\resabstract{%
	I am an engineer and software developer making
	a transition to teaching.
	I have a solid, hands-on understanding of mathematics
	and physics, years of aerospace engineering and software development experience,
	some teaching experience,
	and stories that will help make math real for my students.
}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education and Certifications}

	\begin{reslistx}{Region 13 Educational Service Center}{Austin, TX}
		\ressubitem{Intern Certificate: May, 2018}
		\ressubitem{Projected Completion Date: May, 2019}
	\end{reslistx}

	\begin{reslistx}{TEA Texas Educator Certification}{Austin, TX}
		\ressubitem{Test 243 Physics/Math 7--12 --- passed: May, 2018}
	\end{reslistx}

	\begin{reslistx}{The University of Texas}{Austin, TX}
		\ressubitem{PhD candidate: Aerospace Engineering --- all but dissertation, 1992}
		\ressubitem{MS: Aerospace Engineering, 1988}
	\end{reslistx}

	\begin{reslistx}{The University of Illinois}{Urbana, IL}
		\ressubitem{BS: Aeronatical and Astronautical Engineering --- graduated with \textit{highest honors}, 1982}
		\ressubitem{AB: Political Science --- graduated \textit{magna cum laude}, 1982}
	\end{reslistx}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Teaching Experience}
	\ressubitem{Roth}
	\ressubitem{student teaching}
	\ressubitem{ABC mentoring}
	\ressubitem{ACC}
	\ressubitem{PVAM}
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Previous Employment}

	\begin{ressubsec}{The Advisory Board Company}{Austin, TX}{2012--2018}
		\ressubitem{Architect --- Led system engineering for an enterprise analytics platform.}
		\ressubitem{Development Manager --- Led a big data software team. }
		\ressubitem{Principal Software Engineer --- Designed and built health care software.}
	\end{ressubsec}

	\begin{ressubsec}{L-3 Stratis}{Houston, TX}{2006--2012}
		\ressubitem{Model and Simulation Architect --- Led systems engineering for a multi-team/multi-vendor spacecraft training simulator.}
	\end{ressubsec}

	\begin{ressubsec}{Sun Microsystems}{Austin, TX}{2003--2006}
		\ressubitem{Software Development Team Lead --- Led small, distributed teams building cloud and reliability automation tools.}
	\end{ressubsec}

	\begin{ressubsec}{Titan Systems Corporation}{Houston, TX}{2001--2003}
		\ressubitem{Systems Engineer --- Designed and built software for GPS-based autonomous navigation and grid computing.}
	\end{ressubsec}

	\begin{ressubsec}{The Adrenaline Group}{Austin, TX}{2000--2001}
		\ressubitem{Lead Software Developer --- Technical lead of the small Austin software development team.}
	\end{ressubsec}

	\begin{ressubsec}{LinCom Corporation}{Houston, TX}{1993--2000}
		\ressubitem{Senior Engineer --- Led a team of software developers 
		applying new software technologies into the NASA Mission Control Center. 
		Designed and built real-time systems. Provided project management support to NASA. }
	\end{ressubsec}

\end{ressection}



%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

	\resitem{$\Phi B K$ -- liberal arts honorary, 1982}
	\resitem{$\Sigma T \Gamma$ -- aerospace honorary, 1983}
	\resitem{ISP awards}
	\resitem{NASA Research Fellowship, 1992}
	\resitem{Advisory Board Company Mentor of the Year, 2015}
	\resitem{Neighborhood Plan xxxxxxxx}

\end{ressection}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{References}
	\resitem{Eric Roth --- xxx}
	\resitem{Kyle McVay --- xxx}
	\resitem{Ranga}
	\resitem{Harish Raja --- xxx}
\end{ressection}

\end{document}
